### 2021-02-15 Chapter-3/Chapter-3.tex
init
update

\chapter{Background}

\section{Address-based Side-channel Attacks}

\section{Information Theory}

\section{Binary Analysis}

>>>>

\chapter{Scalable Side-channel Vulnerability Detection}
\section{Motivation}
While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks. According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction. 
\begin{table*}
    \centering
    \caption{Existing leakage detection tool only evaluate them on cryptography library. 1. Most recent work only evaluates their approaches on cryptography libraries. 2. All of them can not reason about the total effect of multiple leakages.}
    \label{table:related_work}

    \begin{tabular}{lllcclc}
    \toprule
    Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
    CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
    CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
    CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
    CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
    DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
    ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
    Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
    ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
    MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
    \bottomrule
    \end{tabular}

    \end{table*}

\section{Threat Model}

\section{Examples}

\section{Math Notations}

\section{Scalability}

\section{Evaluation}

\section{Discussion}
